Dismal Code: Studying the Evolution of Security Bugs

### 2013-09-25 docs/evol.tex
final version

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{array}

@@

We explored the relation between defects with the size of a project
version, measured by the size of its {\sc jar} file by carrying out
correlation tests between the size and the defect counts for each
project and version. The results, all statistically significant ($p
\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
  Security High} category stands out by having a remarkably lower
effect than the other categories}, even {\it Security Low} that nearly
tops the list. As we mentioned earlier, bugs that belong to the
{\it Security High} category are related with
user-input validation issues. Hence, even if a programmer adds
code to a new version, if this code does not requires user
input the possibility of such bug is minimal. 
% dds proposed the following:
%Given that, we could say that it would be productive to search for and fix
%security bugs even if a project grows bigger.

@@

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime, see Figure~\ref{fig:corrplot}. We found significant, but not always
strong, correlations between all pairs. In general, the {\it Security
  High} category showed the weakest correlations with the other
categories. Our results show that in general \textbf{bugs do flock together}.
We do not find projects with only a certain kind of bug; bugs come
upon projects in swarms of different kinds. Bugs of the {\it Security
  High} category, though, are different: they are either not
associated with other bugs, or only weakly so. Perhaps it takes a
special kind of blunder to make it a security hazard.

>>>>

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{array}
\usepackage{color}

\usepackage{ulem}

@@

We explored the relation between defects with the size of a project
version, measured by the size of its {\sc jar} file by carrying out
correlation tests between the size and the defect counts for each
project and version. The results, all statistically significant ($p
\ll 0.05$) can be seen in Table~\ref{tbl:jarsizecorr}.  \textbf{The {\it
  Security High} category stands out by having a remarkably lower
effect than the other categories}, even {\it Security Low} that nearly
tops the list. As we mentioned earlier, bugs that belong to the
{\it Security High} category are related to
user-input validation issues. Hence, even if a programmer adds
code to a new version, if this code does not require user
input, the possibility of such bug is minimal. 
% dds proposed the following:
%Given that, we could say that it would be productive to search for and fix
%security bugs even if a project grows bigger.

@@

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime, see Figure~\ref{fig:corrplot}. We found significant, but not always
strong, correlations between all pairs. In general, the {\it Security
  High} category showed the weakest correlations with the other
categories. Our results show that in general \textbf{bugs do flock together}.
We do not find projects with only a certain kind of bug; bugs come
upon projects in swarms of different kinds. Bugs of the {\it Security
  High} category, though, are different: they are either not
associated with other bugs, or only weakly so. Perhaps it takes a
special kind of blunder to make it a security hazard. Thus, to find such
defects, code reviewers with experience in software security
issues might be needed.
